Generating Lambda Term Individuals in Typed Genetic Programming Using Forgetful A*

### 2013-11-07 tex/evogp13/evogp.tex
evogp13

\usepackage[utf8]{inputenc}
\usepackage{amsfonts}
\usepackage{qtree}
\usepackage{xspace}

@@

\usepackage[ampersand]{easylist}
\usepackage{color}

@@

\newcommand{\Lpr}{\Lambda^\prime}
\newcommand{\ul}[2]{\langle #1 ; #2 \rangle}

\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}

@@

\title{\textit{[něco jako?]} 
Generating lambda term individuals using 
%undisciplined 
forgetful
A*}
\author{Tom\'{a}\v{s} K\v{r}en \and Roman Neruda}
\institute{Matfyz ...}
\maketitle

\begin{abstract}
\textbf{\textit{
(Aby tu něco bylo, pak se udělá lepší 
(tohle je trochu upravenej abstract z diplomky))}}
In this paper, generalization of the standard genetic programming (GP)
for simply typed lambda calculus is presented. We use population 
initialization method parameterized by simple search strategy. 
First described strategy corresponds to standard ramped half-and-half method, 
second one corresponds to exhaustive systematic search and third one is a 
novel geometric strategy, which outperforms standard method in success 
rate, time consumption and average individual size in two experiments. 
Other performance enhancements based on theory of lambda calculus are 
proposed and supported by experiment. Abstraction elimination is 
utilized to enable use of simple tree-swapping crossover.
\end{abstract}

@@

\subsection{gp a typy jsou dobrý / motivace}
...
\subsection{příběh}

(...)\\

Our approach aims to play with the full arsenal given by simply typed lambda calculus, thus we begin our reasoning with an exhaustive systematic search
in mind. Our second goal is to construct a system generalizing Standard 
GP \cite{koza92}.
In order to satisfy both these goals the designed system should be 
parameterized by some simple piece of code that makes the difference
between exhaustive systematic search and standard but 
quiet arbitrary ramped half-and-half generating method.

Those two design goals also differentiate our system from 
the three state of the art systems for typed GP known to us.

~\\(...)

~\\
\textbf{poznamky naky}\textit{\\
- geometrická strategie generování termů jakožto hybrid systematického a náhodného sytylu --- to že jsme si vytičili ty dva cíle který plníme tou 
jednoduchou strategií, tak máme možnost nalízt jednoduchou strategii která 
je na pomezí obou cílů - taková strategie je právě ta naše geometrická 
a ukazuje se že se bohulibě chová právě k strašáku GP -- \textbf{bloatu}.\\
- teoretické LC konstrukty s výhodou použity - @-stromy a eta-redukce\\
- křížení by eliminace 
}

\subsection{obsah kapitol článku v 1 větě}
...

\section{Related work}
\subsection{Yu}
\textbf{Yu} - (články: evenParity, polyGP
\textbf{[doplnit do citací]}
 co sem ted našel, ten o burzách co mám v kindlu)
Odlišnosti:
(1) - generování se nedělá systematicky: pokud strom dojde do místa
kde funkci nemá dát jaký parametr, tak místo tý funkce dá nějaký 
terminál.(uvádí 85\% uspěšnost)  
(2) - Ty křížení ma trochu jinak než v tom článku o even parity,
musim zjistit jak má udělaný že se jí nedostane např prom \#3 někam,
kde neni definovaná když dělá přesun podstromu, v tom starym to ale 
bylo myslim založený na tom, že nedovolovala vnější proměnný uvnitř
lambda termu - což platí i nadále. čili vtom to určitě nehraje full deck.
Naopak se víc zaměřuje na polymorfizmus a další věci.

@@

\section{Preliminaries}
%definice, pojmy

%\subsection{Term}

\Lets 
%Here we  %formally 
describe programming language, 
in which we generate individual programs --- so called \lterms.

@@

\textit{Function application} and 
\textit{$\lambda$-abstraction} are concepts
well known from common programming languages. 
For example in JavaScript 
$(M~N)$ translates to expression \texttt{$M$($N$)} and
$\lamb{x}{M}$ translates to expression \texttt{function($x$)\{return $M$;\}}.
In other words, the function application 
corresponds to the act of supplying a function 
with an argument and
the $\lambda$-abstraction is equivalent to 
\textit{anonymous function}.
%\begin{todo}
% & asi říct o zkratkách notací
%\end{todo}
%
%
%\subsubsection{Reductions}
%(... zmiňovat ? a pokud ano tak tady nebo radši v sekci která diskutuje 
%normálnost vygenerovanejch termů a jejich zkrácení pomocí $eta$-redukce)
%\subsubsection{Tree representations}
%(... zmiňovat ?)
%\subsection{Type}
A \lterm as described above
corresponds to a program expression with no type information
included. Now we will describe \textit{types} (or \textit{type terms}).
After putting those two pieces 
(\textit{\lterms} and \textit{types}) together 
we will get system called \textit{simply typed $\lambda$-calculus}.

@@

%\begin{todo}
% & asi říct o zkratce notace
%\end{todo}

@@

%\begin{todo}
%   & říct že $T \cup F$ v Std GP je u nás $\Gamma$
%   & popsat $\Gamma,x:\tau$ notaci
% a to že to automaticky implikuje že x neni obsažena v $\Gamma$,
% tzn je nová...
%  & že píšem $x:\sigma \in \Gamma$ místo $(x,\sigma) \in \Gamma$
%\end{todo}

@@

%\begin{todo}
%   & Vysvětlit k čemu je to dobrý.
%\end{todo}

\section{Our approach}
\subsection{Introduction}

\begin{todo}
 & úvod ke kapitole - systematicky, A*, filtrace, znova dám do fronty začátek
\end{todo}

@@

At each step, the term $M$ with the smallest size
is pulled from the queue.
According to the actual number of those leafs one of
the following actions is performed.
\begin{enumerate}
 \item If the term $M$ has no unfinished leaf (i.e., it is a finished
 term satisfying \mbox{$\tur{\Gamma}{M}{\tau}$}), then it is added to the
 result collection of generated terms.   
 \item Otherwise, \textit{successors} of the unfinished term $M$ are
       filtered out by \textit{search strategy} $S$ and
       those successors that outlast the filtration 
       are inserted into the queue.
\end{enumerate}

@@

Expansion of the selected unfinished leaf $L$ leads to creation of 
one or many (possibly zero) successors.
In this process, $L$ is replaced
by a new subterm defined by the following rules.
\begin{enumerate}
 \item If $L = \ul{\rho_1 \ar \dots \ar \rho_n \ar \alpha}{\Gamma}$,
 	   where $\alpha$ is atomic type and $n \geq 1$, 
       then $L$ is replaced by 
       $\lamb{x_1 \dots x_n}{\ul{\sigma}
       {\Gamma,x_1 \colon \rho_1,\dots,x_n \colon \rho_n}}$.
       Thus this expansion results in exactly one successor.  
 \item If $L = \ul{\alpha}{\Gamma}$ where $\alpha$ is \textit{atomic} type,
       then for each 
       \mbox{$f : (\tau_1 \ar \dots \ar \tau_m \ar \alpha) \in \Gamma$}
       the unfinished leaf $L$ is replaced by 
       $(~f~(\tau_1,\Gamma)~\dots~(\tau_m,\Gamma)~)$.
       Thus this expansion results in many (possibly zero or one) successors.
\end{enumerate}

@@

\section{Experiments}
\subsection{Simple symbolic regression}

@@

\subsection{Even parity problem}
...
\section{Conclusions}

@@

\begin{thebibliography}{1}

\bibitem{koza92}
  John R. Koza,
  \emph{Genetic Programming: On the Programming of Computers by Means of Natural Selection}.
  MIT Press, Cambridge, MA,
  1992.

\bibitem{koza05}
  Koza, J.R., Keane, M., Streeter, M., Mydlowec, W.,Yu, J., Lanza, G. 
  \emph{Genetic Programming IV: Routine Human-Competitive Machine Intelligence.} 
  Springer, 2005. ISBN 978-0-387-26417-2

\bibitem{fg}
 Riccardo Poli, William B. Langdon, Nicholas F. McPhee
 \emph{A Field Guide to Genetic Programming}.
 Lulu Enterprises, UK Ltd, 2008.

\bibitem{yu01}
  T. Yu. 
  \emph{Hierachical processing for evolving recursive and modular 
        programs using higher order functions and lambda abstractions}. 
  Genetic Programming and Evolvable Machines,
  2(4):345–380, December 2001. ISSN 1389-2576.

\bibitem{montana95}
D. J. Montana. 
\emph{Strongly typed genetic programming.} 
Evolutionary Computation, 3(2): 199–230, 1995.
%URL \url{ http://vishnu.bbn.com/papers/stgp.pdf }. nefacha

\bibitem{haynes96}
T. D. Haynes, D. A. Schoenefeld, and R. L. Wainwright. 
\emph{Type inheritance in strongly typed genetic programming.} 
In P. J. Angeline and K. E. Kinnear, Jr., editors, Advances
in Genetic Programming 2, chapter 18, pages 359–376.
MIT Press, Cambridge, MA, USA, 1996. ISBN 0-262-01158-1. 
%URL \url{http://www.mcs.utulsa.edu/~rogerw/papers/Haynes-hier.pdf}.

\bibitem{olsson94}
J. R. Olsson. 
\emph{Inductive functional programming using incremental program 
transformation and Execution of logic programs by 
iterative-deepening A* SLD-tree search.} 
Dr scient thesis, University of Oslo, Norway, 1994.

\bibitem{kes}
Forrest Briggs, Melissa O’Neill.
\emph{Functional Genetic Programming and Exhaustive
Program Search with Combinator Expressions.}
International Journal of Knowledge-based and Intelligent Engineering Systems,
Volume 12 Issue 1, Pages 47-68, January 2008.

\bibitem{barendregt84}
H. P. Barendregt,
\emph{The Lambda Calculus: its Syntax and Semantics}, 
revised ed., North-Holland, 1984.

\bibitem{barendregt92}
H. Barendregt , S. Abramsky , D. M. Gabbay , T. S. E. Maibaum.
\emph{Lambda Calculi with Types.} 
Handbook of Logic in Computer Science, 1992.

\bibitem{barendregt10}

  Henk Barendregt, Wil Dekkers, Richard Statman,
  \emph{Lambda Calculus With Types}.
  Cambridge University Press,
  2010. 
  %URL \url{http://www.cs.ru.nl/~henk/book.pdf}.

\bibitem{jones87}
Simon Peyton Jones. 
\emph{The Implementation of Functional Programming Languages}. 
Prentice Hall, 1987.

\bibitem{AIAMA}
	Stuart J. Russell, Peter Norvig,
	\emph{Artificial Intelligence: A Modern Approach}.
	Pearson Education,
	2003.

\end{thebibliography}

@@

>>>>

%\usepackage{times}
\usepackage[utf8]{inputenc}
\usepackage{amsfonts}
%\usepackage{qtree}
\usepackage{xspace}

@@

\usepackage[ampersand]{easylist}
\usepackage[usenames,dvipsnames]{color}

@@

\newcommand{\Lpr}{\Lambda^\prime}
\newcommand{\ul}[2]{\langle #1 ; #2 \rangle}
\newcommand{\ro}[1]{{\color{blue} #1}}
\newcommand{\tom}[1]{{\color{ForestGreen} #1}}

%\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}

@@

\title{
Generating Lambda Term Individuals in Typed Genetic Programming Using 
%undisciplined 
Forgetful A*}
\author{Tom\'{a}\v{s} K\v{r}en\inst{1} \and Roman Neruda\inst{2}}
\institute{%
Faculty of Mathematics and Physics\\
Charles University in Prague\\
Malostransk\'e n\'am\v{e}st\'\i~25, 11000 Prague, Czech Republic\\
\email{tomas.kren@mff.cuni.cz}
\and
Institute of Computer Science\\
Academy of Sciences of the Czech Republic\\
Pod Vod\'arenskou v\v{e}\v{z}\'\i~2, 18207, Prague, Czech Republic\\
\email{roman@cs.cas.cz}
}
\maketitle

\begin{abstract}
In this paper, a generalization of genetic programming 
for simply typed lambda calculus is presented. We propose three population 
initialization methods depending on different search strategies. 
The first strategy corresponds to standard ramped half-and-half initialization, 
the second one corresponds to exhaustive systematic search, and the third one 
represents a novel geometric strategy which outperforms standard genetic 
programming in success rate, time consumption and average individual size 
on two experiments. 
Other performance enhancements based on theory of lambda calculus are 
proposed and supported by experiments, including abstraction elimination 
that enables us to utilize a simple tree-swapping crossover.
\end{abstract}

@@

%\subsection{gp a typy jsou dobrý / motivace}
%...
%\subsection{příběh}

%(...)\\

Genetic programming (GP) represents an efficient method for automatic generating of programs by means of evolutionary techniques~\cite{koza92,koza03}. Early attempts to enhance the GP approach with the concept of types include the seminal work~\cite{montana95} where the ideas from Ada programming language were used to define a so-called strongly typed GP.

\begin{todo}
& \ro{... něco k tomu, že se to teda dělá i skrz lambda kalkul}
\end{todo}

The key issue in the lambda calculus approach to enrich GP with types is the method of individual generation. During the expansion phase the set of unfinished terms can be browsed with respect to various search strategies. Our approach to this problem aims to utilize the full arsenal given by the simply typed lambda calculus. Thus, the natural idea is to employ an exhaustive systematic search. On the other hand, if we were to mimic the standard GP approach, a quite arbitrary yet common and successful ramped half-and-half generating heuristic~\cite{fg} should probably be used.  
These two search methods in fact represent boundaries between which we will try to position our parameterized solution that allows us to take advantage of both strategies. This design goal also differentiate our approach from 
the three state of the art proposals for typed GP known to us that are discussed in the following section. 
Our proposed \emph{geometrical search strategy} described in this paper is such a successful hybrid mixture of random and systematic exhaustive search. Experiments show that it is also very efficient dealing with one of the traditional GP scarecrows - the bloat problem.

%~\\(...)
%
%~\\
%\textbf{poznamky naky}\textit{\\
%- geometrická strategie generování termů jakožto hybrid systematického a náhodného sytylu --- to že jsme si vytičili ty dva cíle který plníme tou 
%jednoduchou strategií, tak máme možnost nalízt jednoduchou strategii která 
%je na pomezí obou cílů - taková strategie je právě ta naše geometrická 
%a ukazuje se že se bohulibě chová právě k strašáku GP -- \textbf{bloatu}.\\
%- teoretické LC konstrukty s výhodou použity - @-stromy a eta-redukce\\
%- křížení by eliminace 
%}

%\subsection{obsah kapitol článku v 1 větě}

The rest of the paper is organized as follows: The next section briefly discusses related work in the field of typed GP, while section~\ref{preliminaries} introduces necessary notions. Main original results about search strategies in individual generating are described in section~\ref{approach}. Section~\ref{experiments} presents results of our method on three well-known tasks, and the paper is concluded by section~\ref{conclusions}.

\section{Related work}
\label{related}
\subsection{Yu}
\textbf{Yu} - (články: evenParity, polyGP
\textbf{[doplnit do citací]}
 co sem ted našel, ten o burzách co mám v kindlu)
Odlišnosti:
(1) - generování se nedělá systematicky: pokud strom dojde do místa
kde funkci nemá dát jaký parametr, tak místo tý funkce dá nějaký 
terminál.(uvádí 85\% uspěšnost)  
(2) - Ty křížení ma trochu jinak než v tom článku o even parity,
musim zjistit jak má udělaný že se jí nedostane např prom \#3 někam,
kde neni definovaná když dělá přesun podstromu, v tom starym to ale 
bylo myslim založený na tom, že nedovolovala vnější proměnný uvnitř
lambda termu - což platí i nadále. čili vtom to určitě nehraje full deck.
Naopak se víc zaměřuje na polymorfizmus a další věci.

@@

\section{Preliminaries}
\label{preliminaries}
%definice, pojmy
%\subsection{Term}

In this section, several notions necessary to build a typed GP based on lambda calculus are introduced. 
First, \lets 
%Here we  %formally 
describe a programming language, 
in which the GP algorithm generates individual programs --- the so called \lterms.

@@

\textit{Function application} and 
\textit{$\lambda$-abstraction} are concepts
well known from common programming languages. 
For example in JavaScript 
$(M~N)$ translates to expression \texttt{$M$($N$)} and
$\lamb{x}{M}$ translates to expression \texttt{function($x$)\{return $M$;\}}.
In other words, the function application 
corresponds to the act of supplying a function 
with an argument, and
the $\lambda$-abstraction is equivalent to 
\textit{anonymous function}\footnote{Apart from JavaScript, anonymous functions are common e.g. in Python and Ruby, 
they were recently introduced to C++, and they are expected to be supported in Java 8.}.
\begin{todo}
 & asi říct o zkratkách notací
\end{todo}

%\subsubsection{Reductions}
%(... zmiňovat ? a pokud ano tak tady nebo radši v sekci která diskutuje 
%normálnost vygenerovanejch termů a jejich zkrácení pomocí $eta$-redukce)
%\subsubsection{Tree representations}
%(... zmiňovat ?)
%\subsection{Type}

A \lterm as described above
corresponds to a program expression with no type information
included. Now we will describe \textit{types} (or \textit{type terms}).

@@

\begin{todo}
 & asi říct o zkratce notace
\end{todo}

The system called \textit{simply typed $\lambda$-calculus} is now easily obtained by
combining the previously defined \textit{\lterms} and \textit{types} together.

@@

\begin{todo}
   & říct že $T \cup F$ v Std GP je u nás $\Gamma$
   & popsat $\Gamma,x:\tau$ notaci
 a to že to automaticky implikuje že x neni obsažena v $\Gamma$,
 tzn je nová...
  & že píšem $x:\sigma \in \Gamma$ místo $(x,\sigma) \in \Gamma$
\end{todo}

@@

\begin{todo}
   & Vysvětlit k čemu je to dobrý. Prostě říct že 
     to $\ul{\tau}{\Gamma}$ představuje zatim nespecifikovaný term
     který je ale typu $\tau$ a mohu se v něm objevit stavební symboly
     z $\Gamma$.
\end{todo}

\section{Our approach}
\label{approach}
\subsection{Introduction}
\tom{
Our approach to \lterm gerating is based on technique 
briefly described in \cite{barendregt10}, which generates
well-typed \lterms in their long normal form. 
We use this technique to perform systematic exhaustive enumeration
of \lterms in their long normal form in order from smallest to largest.
We use well known \textit{A* algorithm} \cite{AIMA} for this task.
A* is used to search in a given state space for a goal state. 
It maintains a priority queue to organize states yet to be explored.
Initially this queue contains only the initial state.

Our state space to search in is the space of unfinished \lterms. 
The initial state is the unfinished term $\ul{\tau}{\Gamma}$, 
where $\tau$ is the desired type of
terms to be generated and $\Gamma$ is the context
representing the set of building symbols to be used in construction of
terms (it corresponds to the set $T \cup F$ in
standard GP enriched with types). The process of determining 
successors of a state described below is designed so it constructs well-typed 
\lterms and omits no \lterm in its long normal form. 
A state is considered a goal state if it contains no unfinished
leaf, i.e., it is a finished \lterm.

Our generating method is based on simple modification of the
standard A*, which we call \textit{forgetful A*}. This modification consist in 
additional parameter for the A* algorithm -- the \textit{search strategy}. 
It is a simple filtration function (along with initialization procedure)
that is given the set of all successors of the state that is being examined
and returns a subset of this input. This subset is added to the priority queue 
to be further explored. In this way the search space may be reduced as 
the filtration function may \textit{forget} some successors.
If the queue becomes empty before the desired number of \lterms
is generated, then the initial statete is inserted to the queue
and the process continues. For the standard A* this would be meaningless,
but since our A* is forgetful this kind of restart makes sense.

A* keeps a priority queue of states during the generation process,
on the other hand the \textit{ramped half-and-half method}, 
the standard GP algorithm for generating individuals, 
keeps only one individual which is gradually constructed. This 
behavior is easily achieved by use of suitable search strategy 
that returns subset consisting of only one successor.
The systematic search is obtained by search strategy that 
returns whole input set.      
Our novel \textit{geometric strategy} can be understood as
point somewhere between those two extremes.
}

\begin{todo}
& \tom{Kde nejlíp zmínit citaci diplomky? Něco jako, popisujem to tu velmi ve ztručnosti,
  more elaborate description may be found in [diplomka]?}
& \tom{definovat long normal form? (asi nejde uplně krátce bohužel)}
\end{todo}

@@

At each step, the term $M$ with the smallest size
is pulled from the queue.
According to the number of unfinished leafs in $M$ one of
the following actions is performed.
\begin{enumerate}
 \item If the term $M$ has no unfinished leaf (i.e., it is a finished
 term satisfying \mbox{$\tur{\Gamma}{M}{\tau}$}), then it is added to the
 result set\footnote{
 TODO: říct že tim že je to set se řeší problém toho, aby se tam nevyskytovali
 některý vygenerovaný víckrát, pokud však toto nechcem můžem použít jinou collection
 , případně to vůbec nezminovbat když by to kradlo moc místa
 } of generated terms.   
 \item Otherwise, \textit{successors} of the unfinished term $M$ are
       filtered out by \textit{search strategy} $S$ and
       those successors that outlast the filtration 
       are inserted into the queue.
\end{enumerate}

@@

Expansion of the selected unfinished leaf $L$ leads to creation of 
one or many (possibly zero) successors.
In this process, $L$ is replaced
by a new subterm defined by the following rules.
\begin{enumerate}
 \item If $L = \ul{\rho_1 \ar \dots \ar \rho_n \ar \alpha}{\Gamma}$,
 	   where $\alpha$ is atomic type and $n \geq 1$, 
       then $L$ is replaced by 
       $\lamb{x_1 \dots x_n}{\ul{\alpha}
       {\Gamma,x_1 \colon \rho_1,\dots,x_n \colon \rho_n}}$.
       Thus this expansion results in exactly one successor.  
 \item If $L = \ul{\alpha}{\Gamma}$ where $\alpha$ is \textit{atomic} type,
       then for each 
       \mbox{$f : (\tau_1 \ar \dots \ar \tau_m \ar \alpha) \in \Gamma$}
       the unfinished leaf $L$ is replaced by 
       $(~f~(\tau_1,\Gamma)~\dots~(\tau_m,\Gamma)~)$.
       Thus this expansion results in many (possibly zero or one) successors.
\end{enumerate}

@@

\section{Experiments}
\label{experiments}

\subsection{Simple symbolic regression}

@@

\subsection{Even parity problem}
...

\section{Conclusions}
\label{conclusions}

@@

\nocite{*}

\bibliographystyle{splncs}
\bibliography{gp}

@@

%
%\begin{thebibliography}{1}
%
%
%\bibitem{koza92}
  %John R. Koza,
  %\emph{Genetic Programming: On the Programming of Computers by Means of Natural Selection}.
  %MIT Press, Cambridge, MA,
  %1992. 
%
%\bibitem{koza05}
  %Koza, J.R., Keane, M., Streeter, M., Mydlowec, W.,Yu, J., Lanza, G. 
  %\emph{Genetic Programming IV: Routine Human-Competitive Machine Intelligence.} 
  %Springer, 2005. ISBN 978-0-387-26417-2 
%
%\bibitem{fg}
 %Riccardo Poli, William B. Langdon, Nicholas F. McPhee
 %\emph{A Field Guide to Genetic Programming}.
 %Lulu Enterprises, UK Ltd, 2008.
%
%\bibitem{yu01}
  %T. Yu. 
  %\emph{Hierachical processing for evolving recursive and modular 
        %programs using higher order functions and lambda abstractions}. 
  %Genetic Programming and Evolvable Machines,
  %2(4):345–380, December 2001. ISSN 1389-2576.
%
%
%\bibitem{montana95}
%D. J. Montana. 
%\emph{Strongly typed genetic programming.} 
%Evolutionary Computation, 3(2): 199–230, 1995.
%%URL \url{ http://vishnu.bbn.com/papers/stgp.pdf }. nefacha
%
%\bibitem{haynes96}
%T. D. Haynes, D. A. Schoenefeld, and R. L. Wainwright. 
%\emph{Type inheritance in strongly typed genetic programming.} 
%In P. J. Angeline and K. E. Kinnear, Jr., editors, Advances
%in Genetic Programming 2, chapter 18, pages 359–376.
%MIT Press, Cambridge, MA, USA, 1996. ISBN 0-262-01158-1. 
%%URL \url{http://www.mcs.utulsa.edu/~rogerw/papers/Haynes-hier.pdf}.
%
%\bibitem{olsson94}
%J. R. Olsson. 
%\emph{Inductive functional programming using incremental program 
%transformation and Execution of logic programs by 
%iterative-deepening A* SLD-tree search.} 
%Dr scient thesis, University of Oslo, Norway, 1994.
%
%\bibitem{kes}
%Forrest Briggs, Melissa O’Neill.
%\emph{Functional Genetic Programming and Exhaustive
%Program Search with Combinator Expressions.}
%International Journal of Knowledge-based and Intelligent Engineering Systems,
%Volume 12 Issue 1, Pages 47-68, January 2008. 
%
%
%\bibitem{barendregt84}
%H. P. Barendregt,
%\emph{The Lambda Calculus: its Syntax and Semantics}, 
%revised ed., North-Holland, 1984.
%
%\bibitem{barendregt92}
%H. Barendregt , S. Abramsky , D. M. Gabbay , T. S. E. Maibaum.
%\emph{Lambda Calculi with Types.} 
%Handbook of Logic in Computer Science, 1992. 
%
%\bibitem{barendregt10}
%
  %Henk Barendregt, Wil Dekkers, Richard Statman,
  %\emph{Lambda Calculus With Types}.
  %Cambridge University Press,
  %2010. 
  %%URL \url{http://www.cs.ru.nl/~henk/book.pdf}.
%
%\bibitem{jones87}
%Simon Peyton Jones. 
%\emph{The Implementation of Functional Programming Languages}. 
%Prentice Hall, 1987.
%
%
%\bibitem{AIAMA}
	%Stuart J. Russell, Peter Norvig,
	%\emph{Artificial Intelligence: A Modern Approach}.
	%Pearson Education,
	%2003. 
%
%
%\end{thebibliography}
